The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-09-01 ecology_and_evolution/paper.Rmd
renamed folder

@@

At each iteration of the cross-validation, one fold acts as the test set and the remaining three act as the training set. We fit the model to all focal trees in the training set, apply the model to all focal trees in the test set, compute predicted values, and compute the RMSE. Furthermore, to maintain spatial independence between the test and training sets, a "fold buffer" that extends `r comp_dist`m outwards from the boundary of the test set is considered; all trees within this "fold buffer" are excluded from the training set (see Figure \@ref(fig:scbi-spatial-cross-validation-schematic).

>>>>

Running head: `forestecology` R package

@@

At each iteration of the cross-validation, one fold acts as the test set and the remaining three act as the training set. We fit the model to all focal trees in the training set, apply the model to all focal trees in the test set, compute predicted values, and compute the RMSE. Furthermore, to maintain spatial independence between the test and training sets, a "fold buffer" that extends `r comp_dist`m outwards from the boundary of the test set is considered; all trees within this "fold buffer" are excluded from the training set (see Figure \@ref(fig:scbi-spatial-cross-validation-schematic)).
